---
title: "How Melburnians walk during COVID-19"
author: "Panagiotis Stylianos"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Introduction

In this document we examine the walking frequency of Melburnians during the July
lockdown.  
The data are provided in the __rwalkr__ package.

```{r libraries, include=FALSE}
library(tidyverse)
library(rwalkr)
```



```{r data, include=FALSE}
starting_day <- as.Date('2020-07-08')

steps <- rwalkr::melb_walk(from = starting_day, to = Sys.Date() - 1L)

```


#### Plot of Total Steps per Day


```{r plot, echo=FALSE, message=FALSE,include=TRUE, fig.height= 2, fig.align="left"}
steps %>% 
  group_by(Date) %>% 
  summarise(TotalSteps = sum(Count, na.rm = T)) %>% 
  ggplot(aes(Date, TotalSteps)) +
    geom_line()
```

#### Table of five most active sensors

```{r sensors, echo=FALSE, include=TRUE, message=FALSE, warning=FALSE}
steps %>% 
  group_by(Sensor) %>% 
  summarise(TotalSteps = sum(Count, na.rm = T)) %>% 
  mutate(Proportion = round(TotalSteps/sum(TotalSteps) * 100, 2)) %>% 
  arrange(desc(Proportion)) %>% 
  head(5)
```
#### Formula for proportion

$y_{i}$ = $x_{i}/\sum_{i=1}^{`r nrow(steps)`} x_{i}$

where $x_{i}$ is the total steps monitored by this sensor,
$sum_{i=1}^{`r nrow(steps)`} x_{i}$ is the total steps monitored by all sensors. and $y_{i}$ is the proportion that each sensor contributed to the dataset.

#### Table of Packages and functions used in the report

Library  | Functions
---------|-----------------------
base     | as.Date(), Sys.Date(), sum()
dplyr    | group_by(), summarise(), mutate(), arrange()
ggplot2  |ggplot(), aes(), geom_line()
rwalkr   |melb_walk()  
            
